Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-23 paper/manuscript.tex
very rough outline of Discussion

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/prefs_fracsurvive/prefs_fracsurvive_logoplots.pdf}}
\caption{
\label{fig:muttolerance}
{\bf Mutational tolerance of HA sites in the antibody-binding footprints.}
These plots show all HA sites within 4 angstroms of the antibody in the crystal structure, plus any additional sites (marked with a *) where we identified antigenic mutations. 
The logo plots at bottom show the preference of each HA site for each amino acid under selection for viral growth as measured by \citet{doud2016accurate}.
For instance, site 153 in HA only tolerates tryptophan, so W occupies the entire height of the preference logo stack.
In contrast, site 156 tolerates many amino acids, all of which contribute to the height of the preference logo stack. 
Above the preference logo stacks are logo plots showing the excess fraction surviving antibody treatment as measured in the current study.
Note that scale for these antigenic effects is 10$\times$ smaller for the FI6v3 and C179 than for S139/1.
Overall, it is clear that many mutations that are tolerated at footprint sites that do not have a detectable antigenic effect.
}
\end{figure}

@@

\section*{DISCUSSION}
Some discussion

>>>>

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/prefs_fracsurvive/prefs_fracsurvive_logoplots.pdf}}
\caption{
\label{fig:muttolerance}
{\bf Mutational tolerance of HA sites in the antibody-binding footprints.}
These plots show all HA sites within 4 angstroms of the antibody in the crystal structure, plus any additional sites (marked with a *) where we identified antigenic mutations. 
The logo plots at bottom show the preference of each HA site for each amino acid under selection for viral growth as measured by \citet{doud2016accurate}.
For instance, site 153 only tolerates tryptophan, so W occupies the entire height of the preference logo stack.
In contrast, site 156 tolerates many amino acids, all of which contribute to the height of the preference logo stack. 
Above the preference logo stacks are logo plots showing the excess fraction surviving antibody treatment as measured in the current study.
Note that scale for these antigenic effects is 10$\times$ smaller for the FI6v3 and C179 than for S139/1.
Overall, it is clear that many mutations are tolerated at footprint sites but do not have a detectable antigenic effect.
}
\end{figure}

@@

\section*{DISCUSSION}
We have quantified the ease of escape.
There are clear differences among antibodies
Stalk antibodies are harder to escape.

However, despite the lack of strong escape for stalk, there are small-effect antigenic mutations.
Points to an advantage over the classical approach which requires large effect.
Also, it's nice that when we don't find anything we can make statements about what exists.

Interesting that breadth does not directly associate with ease of escape.

Important caveat is that we are looking at the effects of single mutations in the background of A/WSN/1933.
Things could be different in other backgrounds and/or with combinations~\citep{gong2013stability,harms2014historical,starr2017alternative}.
\citet{wu2017diversity}.
Nonetheless, given that HA antigenic drift mostly involves point mutations...

Overall, we have described a new hybrid experimental-analytical approach to quantify antigenic effects.
Useful both for characterizing the epitopes and escape mutants for single antibodies, but more importantly for comparing across antibodies.
As antibodies are increasingly considered for anti-viral therapeutics, the ability to comprehensively quantify the potential for viral escape will be useful
